Cluster Detection from three-dimensional Lensing Mass Map

### 2021-01-08 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
small revision on paper

Following \citet{WL-massMap-Glimpse2D-Lanusse2016}, we normalize the detected
peaks in the $l$-th ($l=1...20$) lens redshift plane to account for the peak
amplitude difference due to the difference in the norm of the lensing kernels
for different redshift bins:
\begin{equation}
\delta^{\rm{n}}_{\rm{peak}}(\vec{\theta},z_l)=\delta_{\rm{peak}}(\vec{\theta},z_l)/\mathcal{R}_{l}^{\frac{1}{2}},
\end{equation}
where the normalization matrix is defined as
\begin{equation}
\mathcal{R}_{l}=\sum_s K^2(z_l,z_s).
\end{equation}
The solid steps in Figure \ref{fig_peakHist} show the histograms of the
normalized peaks with different penalization parameters. Also, we simulate
$1000$ realizations of pure noise catalogs and perform the reconstructions on
these noise catalogs to study the noise properties. The dashed steps in Figure
\ref{fig_peakHist} show the histograms of normalized peaks detected from the
pure noise catalogs. The solid lines in Figure \ref{fig_peakHist} show the
best-fit Gaussian distributions to the noise peaks' histograms.

>>>>

Following \citet{WL-massMap-Glimpse2D-Lanusse2016}, we normalize the detected
peaks in the $l$-th ($l=1...20$) lens redshift plane to account for the peak
amplitude difference due to the difference in the norm of the lensing kernels
for different redshift bins:
\begin{equation}
\delta^{\rm{n}}_{\rm{peak}}(\vec{\theta},z_l)=\delta_{\rm{peak}}(\vec{\theta},z_l)/\mathcal{R}_{l}^{\frac{1}{2}},
\end{equation}
where the normalization matrix is defined as
\begin{equation}
\mathcal{R}_{l}=\sum_s K^2(z_l,z_s).
\end{equation}
In Figure \ref{fig_peakHist}, we show the stacked histograms of the
normalized peaks with different penalization parameters. Here, we stack the
histograms from $100$ realizations of all halos sampled in the redshift-mass
plane.
Also, we simulate $1000$ realizations of pure noise catalogs and perform the
reconstructions on these noise catalogs to study the noise properties.  The
histograms of normalized peaks detected from the pure noise catalogs are shown
in Figure \ref{fig_peakHist} and we show the best-fit Gaussian functions of the
noise peaks' histograms.
